\begin{tabularx}{\linewidth}{|c|X|c|}
  \hline
  Parameter & Source & Value\\
  \hline
  \acs{k}  & \acf{k} & 0.5\\
  fullCanAge [yr] & Year where tree reaches full Canopy Cover. & 0  \\
  kG \reciprocal\kilo\pascal & Determines the response of the canopy conductance to the vapor pressure deficit. & 0.5\\
  alpha [\kilogram\mole] & Canopy quantum efficiency. & 0.06\\
  \hline
  \acs{fT} [frac] & The parameters specifing limitations from ambient temperature. & \\
  $mn_{\acs{fT}}$ [\Celsius] & The minimum temperature for respiration & 5\\
  $opt_{\acs{fT}}$ [\Celsius] & The optimum temperature for respiration & 20\\
  $mx_{\acs{fT}}$  [\Celsius] & The maximum temperature for respiration & 40\\
  \hline
  \acs{BLcond} [\reciprocal\meter] & Canopy boundary layer conductance. Used in the calcuation of transpiration & 0.2\\
  \hline
  \acs{fAge} [frac] & Specifies the growth limiter as a function of the tree age.  This is a time dependant parameter. Specified with 4 parameters. & \\
  $f0_{\acs{fAge}}$ &  Value for \acs{fAge} at Initial Time & 1\\
  $f1_{\acs{fAge}}$ & Value for \acs{fAge} at Infinite Time & 0 \\
  $tm_{\acs{fAge}}$ [y] & Time in years where value is the average of $f0$ and $f1$ & 47.5\\
  $n_{\acs{fAge}}$ & $n>=1$ Parameter specifing the rate of change around tm.  n=1 is approximately a linear change, as n increases, change becomes more localized around tm. & 3.5\\
  \hline
   $fN0$ [frac] & Used in the calculation of the nutritional modifier,$fNutr$.  $fNutr$ ranges from [$fNO$,1) based on the fertility index which ranges from 0 to 1.  When $fN0=1$ indicates $fNutr=1$ & 1\\
   \hline
   \acs{SLA} [$\square\meter\per\kilogram$] & \acf{SLA}.  Defined as a function of the tree age.  Used in the calculation of LAI. &\\
   $f0_{\acs{SLA}}$ & \acs{SLA} at initial time & 10.8\\
   $f1_{\acs{SLA}}$ & \acs{SLA} at infinite timestep & 10.8\\
   $tm_{\acs{SLA}}$ [y] & Time in years where value is the average of $f0$ and $f1$ & 1\\
   $n$  & $n>=1$; Parameter specifing the rate of change around $tm$.  $n=1$ is approximately a linear change, as n increases, change becomes more localized around $tm$. & 2\\
   \hline
   $Cond$ [$\meter\per\second$] &  Canopy Conductance.  Along with a Physiological modifer, specifies the canopy conductance.  Used in calculation of transpiration & \\
   $mn_{Cond}$ & Minimum value, when $lai=0$ & 0.0001\\
   $mx_{Cond}$ & Maximum value & 0.02\\
   $lai_{Cond}$ [$\square\meter\per\square\meter$] & \ac{LAI} where parameter reaches a maximum value. & 3.33\\
 \hline
 $Intcptn$ [frac] & Rainfall interception fraction.  A linear function w.r.t. \ac{LAI} & \\
  $mn_{Intcptn}$ & Minimum value, when lai=0 & 0\\
  $mx_{Intcptn}$ & Maximum value & 0.15\\
  $lai_{Intcptn}$ [$\square\meter\per\square\meter$] & \ac{LAI} where parameter reaches a maximum value. & 5\\
 \hline \hline
 y & Assimilation use efficiency.  Used in calculation of the NPP. & 0.47\\
 \hline 
\end{tabularx}

